1st Revision

### 2019-03-31 Report/first-revision.Rmd
Adds more pointing graphs

### Experiment 2 phase 1
```{r}
summary(aov(abs_error ~ learning.condition, data = sub_sop_all_2[sub_sop_all_2$phase == 2, ]))
ggplot(sub_sop_all_2[sub_sop_all_2$phase == 1, ], aes(learning.condition, abs_error)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

@@

@@

@@

>>>>

```{r}
ggplot(sub_sop_all, aes(learning.condition, abs_error, group=factor(phase), fill=factor(phase))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
ggplot(sub_sop_all, aes(factor(phase), abs_error, group=learning.condition, fill=learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

### Experiment 2 phase 1
```{r}
summary(aov(abs_error ~ learning.condition, data = sub_sop_all_2[sub_sop_all_2$phase == 1, ]))
ggplot(sub_sop_all_2[sub_sop_all_2$phase == 1, ], aes(learning.condition, abs_error)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

@@

```{r}
ggplot(sub_sop_all_2, aes(learning.condition, abs_error, group=factor(phase), fill=factor(phase))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
ggplot(sub_sop_all_2, aes(factor(phase), abs_error, group=learning.condition, fill=learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

@@

```{r}
ggplot(sop_all, aes(learning.condition, abs_error, group=factor(phase), fill=factor(phase))) +
  facet_wrap(~testing.condition)+
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
ggplot(sop_all, aes(factor(phase), abs_error, group=learning.condition, fill=learning.condition)) +
  facet_wrap(~testing.condition)+
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

@@

###
```{r}
ez_point <- sop_all[complete.cases(sop_all),]
ez_point$phase <- as.factor(ez_point$phase)
ezANOVA(ez_point,
        within = .(phase),
        between = .(learning.condition),
        dv=abs_error,
        wid=id
        )
```
